Retrofitting Effect Handlers onto OCaml

### 2020-11-17 retro-concurrency.tex
edits

For stack walking during GC, the only change necessary was to make the runtime
aware of fiber layout and how to follow the parent pointers. The stack map
generation and scanning each frame for roots remains the same. Sivaramakrishnan
et al.~\cite{Sivaramakrishnan20} present the challenges and solutions for
integrating fibers with the concurrent mark-and-sweep GC of Multicore OCaml.

@@

In this section, we evaluate the performance of Multicore OCaml effect handlers
against the performance requirements set in \S\ref{sec:req}. Multicore OCaml is
an extension of 4.10.0 OCaml compiler with support for shared memory
parallelism and effect handlers. These results were obtained on 2-socket,
Intel\textregistered Xeon\textregistered Gold 5120 x86-64 server, with 28
physical cores (14 cores on each socket), and 2 hardware threads per core. Each
core runs at 2.20GHz and has 32 KB of L1 data cache, 32 KB of L1 instruction
cache and 1MB of L2 cache. The cores on a socket share a 19.25 MB L3 cache. The
server has 64GB of main memory and runs Ubuntu 18.04.

>>>>

For stack walking during GC, the only change necessary was to make the runtime
aware of fiber layout and how to follow the parent pointers. The stack map
generation and scanning each frame for roots remains the same. The
challenges and solutions for integrating fibers with the concurrent
mark-and-sweep GC of Multicore OCaml have been discussed previously~\cite{Sivaramakrishnan20}.

@@

In this section, we evaluate the performance of Multicore OCaml effect handlers
against the performance requirements set in \S\ref{sec:req}. Multicore OCaml is
an extension of the 4.10.0 OCaml compiler with support for shared memory
parallelism and effect handlers. These results were obtained on 2-socket,
Intel\textregistered Xeon\textregistered Gold 5120 x86-64 server, with 28
physical cores (14 cores on each socket), and 2 hardware threads per core. Each
core runs at 2.20GHz and has 32 KB of L1 data cache, 32 KB of L1 instruction
cache and 1MB of L2 cache. The cores on a socket share a 19.25 MB L3 cache. The
server has 64GB of main memory and runs Ubuntu 18.04.
